\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{parskip} % Removes indent
\usepackage{amssymb} % Includes check mark 

\title{MAP4C Summative}
\author{Eric Taylor}
\date{June 2017}

\begin{document}

\topmargin=0pt % Sets top margin to 0pt
\headheight=0pt % Sets header distance to 0pt
\headsep=0pt % Sets distance between header and body to 0pt
\footskip=0pt % Sets footer to 0pt
\textheight=700pt % Sets height of body to 700pt

\setlength{\parindent}{0pt} % Removes indent

\maketitle \thispagestyle{empty}

\textbf{{\huge Finding Math in Your Career}}

\textbf{\emph{\textsc{1. State the career that you intend on pursuing.}}}

I intend on pursuing a career in web development and computer programming.

\textbf{\emph{\textsc{2. Give a brief description of what you would do on a day-to-day basis in your career.}}}

The beautiful thing about computer programming is that my day-to-day has such a variety of things to do, what I do changes daily. A typical day could look like this: check email, load up necessary tools for today's tasks, check the automated build system and make sure it isn't failing, look at tasks such as bug reports and feature improvements, pick one and work on it or continue working on what was done the previous day, and possibly a meeting or code review / discussion about implementation of solutions for tasks.

\textbf{\emph{\textsc{3. How will you use mathematics and the concepts you have learned in this course in your future career? The units studied in this course are listed below. Place a check mark beside each unit that applies to your career and give a briefly describe how.}}} 

\begin{tabular}{l l}
    \makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$} 1-Variable Statistics 
    &
    \makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$} Personal Finance
    \\
    \makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$} 2-Variable Statistics 
    &
    \makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$} Geometry
    \\
    \makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$} Exponentials
    &
    \makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$} Trigonometry
\end{tabular}

Since it is possible to create a program to do all the math covered in this course, all of the units and concepts covered in this course can apply to the career.

\textbf{\emph{\textsc{4. Contact(Hint: e-mail makes a lot of sense) someone who is currently working in your chosen career and ask them questions about their daily routines and in particular, to explain how they use mathematics in their career.}}}

Contact person: Randy Taylor

[REFER TO INTERVIEW]








\end{document}
